Documentation of Scripts for Generating Random MISDP Instances

### 2020-11-10 RIP-MISDP-Paper/scripts/RandomInstancesMISDP.tex
correct and update random instances and RIP instances document

Kobayashi and Takano~\cite{Kob20} create random instances
of~\eqref{eq:DualMISDP} as follows:
\begin{align*}
  y_k &\sim \unif(\{0,1\}), \, k \leq m_b,\\
  y_k &\sim \unif([0,1]),\, k > m_b, \\
  A^{(k)}_{i,j} &\sim \unif([-1,1]),\, 1\leq j \leq i \leq n, k \in [m],\\
  A^{(0)} &= \sum_{i=1}^m A^{(k)}y_k - \alpha \id,\\
  b_k &= A^{(k)}\bullet \id, \; k \in [m],
\end{align*}
so that~$\sum_{k=1}^m A^{(k)}y_k - A^{(0)} = \alpha\id \succeq 0$
for~$\alpha \geq 0$. They use the following parameters:
\begin{table}[h]
  \centering
  \begin{tabular}{cccc}
    $n$ & $m_c$ & $m_b$ & $\alpha$ \\
    \toprule
    30 & 30 & 30 & $\{1.0,0.1,10\}$ \\
    45 & 45 & 45 & 1.0 \\
    60 & 60 & 60 & 1.0 \\
    $\{15,60\}$ & 30 & 30 & 1.0 \\
    30 & $\{15,60\}$ & 30 & 1.0 \\
    30 & 30 & $\{15,60\}$ & 1.0
  \end{tabular}
\end{table}

The
script~\textsf{SCIPSDP/tools/InstanceGeneration/generateRandomMISDP.prl}
takes as input~$(n,m_b,m_c,\alpha)$ and generates the
instance~\textsf{randomMISDP\_n\_mb\_mc\_alpha.cbf} of the
form~\eqref{eq:DualMISDP} in the CBF-format,
see~\url{http://cblib.zib.de/}.

@@

Li and Xie~\cite{LiX20} propose two valid inequalities for strengthening the MISDP:
\begin{align*}
  \sum_{j=1}^n X_{ij}^2 &\leq X_{ii}z_i,\quad \forall \; i \in [n],\\
  \big(\sum_{j=1}^n \abs{X_{ij}}\big)^2 &\leq kX_{ii}z_i, \quad \forall \;
                                          i \in [n].
\end{align*}
Both inequalities are SOC-representable and can thus be formulated as an SDP-constraint:
\begin{align}\label{eq:ValidSOCPineqSDP}
  \sum_{j=1}^n X_{ij}^2 \leq X_{ii}z_i \; \Leftrightarrow \;
  \begin{pmatrix}
    \tfrac{X_{ii}+z_I}{2} & X_{i1} & \cdots & X_{in} & \tfrac{X_{ii}-z_i}{2}
    \\
    X_{i1} & 1 & & 0 & 0 \\
    \vdots &\vdots & \ddots & \vdots & \vdots \\
    X_{in} & 0 & & 1 & 0 \\
    \tfrac{X_{ii}-z_i}{2} & 0 & \cdots & 0 & 1
  \end{pmatrix} \succeq 0.
\end{align}
This gives rise to the following weaker inequalities:
\begin{align*}
  \sum_{j=1}^n X_{ij}^2 \leq z_i^2 \; \Leftrightarrow \;
  \begin{pmatrix}
    z_i & X_{i1} & \cdots & X_{in} \\
    X_{i1} & 1 & & 0 \\
    \vdots &\vdots & \ddots & \vdots \\
    X_{in} & 0 & & 1
  \end{pmatrix} \succeq 0, \qquad
                   X_{ij}^2 \leq z_iX_{ii}  \; \Leftrightarrow \;
                   \begin{pmatrix}
                     z_i & X_{ij} \\
                     X_{ij} & X_{ii}
                   \end{pmatrix} \succeq 0,
\end{align*}
where the second inequality can be added for all~$0\leq j < i\leq n$.

@@

  \item ``socp''          : 1 (with valid inequalities from~\cite{LiX20}, see~\eqref{eq:ValidSOCPineqSDP}), 0 (without)

@@

    if~$A \geq 0$ entrywise), 0 (with)

@@

\subsection{CBF-file for dual MISDP-formulation of RIP}
\label{sec:CBFdual}
This section describes the structure of the CBF-file for the
MISDP-formulation~\eqref{eq:MISDPRIP} in dual form (using scalar variables)
generated by
\textsf{SCIPSDP/RIP-MISDP-Paper/scripts/RIPCBFdual.m}.\\

@@

\# cons: $2n^2+n+2 - {\color{blue}\text{strgbnds}\cdot n^2}$, \qquad
\# cones = $5 - {\color{blue} \text{strgbnds}}$\\
{\color{violet} If ``boundver'' = 0 : \# cons: $3n+2 - \text{strgbnds}\cdot n$} \\

@@

    &\text{L-}  &1\; {\color{violet}(1)} \qquad & \sum z_i - k \leq 0

@@

\# entries: $4n^2+3n - {\color{blue} \text{strgbnds}\cdot 2n^2}$ \\
{\color{violet} If ``boundver'' = 0 : \# entries: $7n -
  \text{strgbnds}\cdot 2n$. In this case, all constraints are only added

@@

  that $n^2$ needs to be subtracted from the first column
  (scalar cons $i$) in the fourth to seventh line.}

@@

    & n+in+j \quad & i \quad & -1.0\; (i = j),\,
    {\color{orange} -\tfrac{1}{2}\; (i\neq j)} \quad & {\color{blue}-z_j -
      X_{ij} \leq 0}

@@

    & n+in+j \quad & n+\tfrac{1}{2}i(i+1)+j \quad & -1.0
    \quad & {\color{blue}-z_j - X_{ij} \leq 0} \quad & 0 \leq i,\, j \leq

@@

    & n+in+j \quad & n+\tfrac{1}{2}j(j+1)+i \quad & -1.0
    \quad & {\color{blue}-z_j - X_{ij} \leq 0} \quad & 0 \leq i,\, j \leq

@@

    & n+n^2+in+j \quad & i \quad & 1.0\; (i
    = j),\, {\color{orange} \tfrac{1}{2}\; (i\neq j)} \quad & z_j - X_{ij} \geq 0
    \quad & 0

@@

    & n+n^2+in+j \quad &
    n+\tfrac{1}{2}i(i+1)+j \quad & -1.0 \quad & z_j - X_{ij} \geq 0 \quad &

@@

    & n+n^2+in+j \quad &
    n+\tfrac{1}{2}j(j+1)+i \quad & -1.0 \quad & z_j - X_{ij} \geq 0 \quad &

@@

    i = 0,\dots,n-1

@@

\textbf{BCOORD} (scalar cons $i$ | val) \\
\# entries: $n+2$ \\
{\color{violet} If ``boundver'' = 0 : then all constraints are only added
  that $n^2$ needs to be subtracted from the first column
  (scalar cons $i$) in the second and third line.}
    & i \quad & 1.0 \quad & -z_i + 1 \geq 0 \quad & i = 0,\dots,n-1 \\
    & n+2n^2 \quad & -1.0 \quad & \tr(X) - 1 = 0 \quad & i = 0,\dots,n-1
    \\
    & n+2n^2+1 \quad & -k  \quad & \sum z_i - k \geq 0 \quad & i =
    0,\dots,n-1
\textbf{HCOORD} (psd cons $i$ | scalar var $j$ | row | col | val) \\
\# entries: $\tfrac{1}{2}n(n+1)$ {\color{red} $(+n(n+4))$} \\
    &0 \qquad &n+\tfrac{1}{2}i(i+1)+j \qquad &i \qquad &j \qquad &1.0
    \qquad &X \succeq 0 \qquad &0 \leq j \leq i \leq n-1 \\
    &{\color{red}i+1} \qquad &{\color{red}i} \qquad &{\color{red}0} \qquad
    &{\color{red}0} \qquad &{\color{red}\tfrac{1}{2}} \qquad
    &{\color{red}P_i \succeq 0} \qquad & \\
    &{\color{red}i+1} \qquad &{\color{red}i} \qquad &{\color{red}n+1} \qquad
    &{\color{red}0} \qquad &{\color{red}-\tfrac{1}{2}} \qquad
    &{\color{red}P_i \succeq 0} \qquad &\\
    &{\color{red}i+1} \qquad &{\color{red}n+\tfrac{1}{2}i(i+1)+i} \qquad &{\color{red}0} \qquad
    &{\color{red}0} \qquad &{\color{red}\tfrac{1}{2}} \qquad
    &{\color{red}P_i \succeq 0} \qquad &\\
    &{\color{red}i+1} \qquad &{\color{red}n+\tfrac{1}{2}i(i+1)+i} \qquad &{\color{red}n+1} \qquad
    &{\color{red}0} \qquad &{\color{red}\tfrac{1}{2}} \qquad
    &{\color{red}P_i \succeq 0} \qquad &\\
    &{\color{red}i+1} \qquad &{\color{red}i} \qquad &{\color{red}0} \qquad
    &{\color{red}0} \qquad &{\color{red}\tfrac{1}{2}} \qquad
    &{\color{red}P_i \succeq 0} \qquad &\\
    &{\color{red}i+1} \qquad &{\color{red}n+\tfrac{1}{2}i(i+1)+j} \qquad &{\color{red}j+1} \qquad
    &{\color{red}0} \qquad &{\color{red}1.0} \qquad
    &{\color{red}P_i \succeq 0} \qquad &{\color{red}0 \leq j \leq i}\\ 
    &{\color{red}i+1} \qquad &{\color{red}n+\tfrac{1}{2}j(j+1)+i} \qquad &{\color{red}j+1} \qquad
    &{\color{red}0} \qquad &{\color{red}1.0} \qquad
    &{\color{red}P_i \succeq 0} \qquad &{\color{red}i < j \leq
      n-1 }
{\color{red}\textbf{DCOORD} (psd cons $i$ | row | col | val) \\
  \# entries: $n(n+1)$\\
      {\color{red} i+1} \qquad & {\color{red} j+1} \qquad & {\color{red}
        1.0} \qquad & {\color{red} P_i \succeq 0} \qquad & {\color{red} i =
        0, \dots, n-1}

@@

Options in \textsf{SCIPSDP/RIP-MISDP-Paper/scripts/RIPCBFdual.m}:
\begin{itemize}
\item If Rank = 1: \textcolor{green}{PSDCONRANK1} is added.
\item If trineq = 1: In CON the definition of the cone for the trace
  constraint is changed from~$\text{L}=$ to~\textcolor{cyan}{$\text{L-}$}
  or~\textcolor{cyan}{$\text{L}+$}, respectively.
\item If boundver = 0: The coupling constraints are only added for~$i = j$,
  i.e., {\color{violet} $-z_i \leq X_{ii} \leq z_i$, $i \in [n]$}. This
  changes the number of constraints in CON, and the number of entries in
  ACOORD, since all entries with $i \neq j$ in ACOORD need to be
  cancelled. Additionally, the first column (scalar cons $i$) in ACOORD and
  BCOORD needs to be adapted. See the changes in
  \textcolor{violet}{violet}.
\item If boundver = 2: {\color{orange}
    $-\tfrac{1}{2}z_j \leq X_{ij} \leq \tfrac{1}{2}z_j$ for $i \neq j$} is
  weakened to {\color{orange}$-z_j \leq X_{ij} \leq z_j$}, so that the
  {\color{orange} $-\tfrac{1}{2}$} is changed to $-1.0$ in ACOORD.
\item If strgbnds = 1: If A is nonnegative, then the stronger lower
  bounds~$X_{ij} \geq 0$ for all $i,j =0,\dots,n-1$ are used. See the
  changes in \textcolor{blue}{blue} for VAR, CON. Additionally, the two
  lines in ACOORD with a \textcolor{blue}{blue constraint} are cancelled
  as well.
\item If socp = 1: The valid SOCP inequalities
  $\sum_{j=0}^{n-1}X_{ij}^2 \leq X_{ii}z_i$ for $i = 0,\dots,n-1$
  from~\cite{LiX20} are added. See the changes in PSDCON, HCOORD, DCOORD in
  \textcolor{red}{red}. These inequalities are SDP-representable via
  \begin{align*}
    \sum_{j=1}^n X_{ij}^2 \leq X_{ii}z_i \; \Leftrightarrow \;
    P_i \define \begin{pmatrix}
      \tfrac{X_{ii}+z_I}{2} & X_{i1} & \cdots & X_{in} & \tfrac{X_{ii}-z_i}{2}
      \\
      X_{i1} & 1 & & 0 & 0 \\
      \vdots &\vdots & \ddots & \vdots & \vdots \\
      X_{in} & 0 & & 1 & 0 \\
      \tfrac{X_{ii}-z_i}{2} & 0 & \cdots & 0 & 1
    \end{pmatrix} \succeq 0.
  \end{align*}
  See the last two columns in FCOORD, ACOORD, BCOORD for a description on
  how to write these inequalities in the CBF-format. Here, $E_{ij}$ is a
  symmetric matrix of suitable dimension with ones at positions $(i,j)$ and
  $(j,i)$, and zeros else.
\end{itemize}

\subsection{CBF-file for primal MISDP-formulation of RIP}
\label{sec:CBFprimal}
This section describes the structure of the CBF-file for the
MISDP-formulation~\eqref{eq:MISDPRIP} in primal form (using matrix variables)
generated by
\textsf{SCIPSDP/RIP-MISDP-Paper/scripts/RIPCBFdual.m}.\\

@@

\# cons: $2n^2+n+2 + {\color{red}\text{socp}\cdot(\tfrac{1}{2}n(n+3)(n+2))} - {\color{blue}
    \text{strgbnds} \cdot (\tfrac{1}{2}n(n-1))}$, \qquad
\# cones = $5 \quad {\color{red} (6)}$\\

@@

  \text{socp}\cdot(\tfrac{1}{2}n(n+3)(n+2))$} \\

@@

    &\text{L-}  &1 \qquad & \sum z_i - k \leq 0

@@

\# entries: $2n^2+n$ + {\color{red} $\text{socp} \cdot
  n\cdot(3n+5+\tfrac{1}{2}n(n+1))$ } - {\color{blue} $\text{strgbnds} \cdot

@@

{\color{violet} If ``boundver'' = 0: \# entries: $3n + \text{socp} \cdot
  n\cdot(3n+5+\tfrac{1}{2}n(n+1)) - \text{strgbnds} \cdot

@@

{\color{red} The following entries need to be added for all~$i = 0,\dots,n-1$}:

@@

    \leq 0 \quad & i = 0,\dots,n-1

>>>>

Kobayashi and Takano~\cite{Kob20} create random instances
of~\eqref{eq:DualMISDP} as follows:
\begin{align*}
  y_k &\sim \unif(\{0,1\}), \, k \leq m_b,\\
  y_k &\sim \unif([0,1]),\, k > m_b, \\
  A^{(k)}_{i,j} &\sim \unif([-1,1]),\, 1\leq j \leq i \leq n, k \in [m],\\
  A^{(0)} &= \sum_{i=1}^m A^{(k)}y_k - \alpha \id,\\
  b_k &= A^{(k)}\bullet \id, \; k \in [m],
\end{align*}
so that~$\sum_{k=1}^m A^{(k)}y_k - A^{(0)} = \alpha\id \succeq 0$
for~$\alpha \geq 0$. They use the following parameters:
\begin{table}[h]
  \centering
  \begin{tabular}{cccc}
    $n$ & $m_c$ & $m_b$ & $\alpha$ \\
    \toprule
    30 & 30 & 30 & $\{1.0,0.1,10\}$ \\
    45 & 45 & 45 & 1.0 \\
    60 & 60 & 60 & 1.0 \\
    $\{15,60\}$ & 30 & 30 & 1.0 \\
    30 & $\{15,60\}$ & 30 & 1.0 \\
    30 & 30 & $\{15,60\}$ & 1.0
  \end{tabular}
  \caption{Parameters used by Kobayashi and Takano~\cite{Kob20}}.
  \label{tab:KTinstanceSizes}
\end{table}

The
script~\textsf{SCIPSDP/tools/InstanceGeneration/generateRandomMISDP.prl}
takes as input~$(n,m_b,m_c,\alpha,\ell)$ and generates~$\ell$ random
instances~\textsf{randomMISDP\_n\_mb\_mc\_alpha\_k.cbf}
for~$k = 1,\dots,\ell$ of the form~\eqref{eq:DualMISDP} in the CBF-format,
see~\url{http://cblib.zib.de/}. The
script~\textsf{SCIPSDP/tools/InstanceGeneration/generateInstances.sh} can
be used to generate such instances using the parameters from
Table~\ref{tab:KTinstanceSizes}.

@@

Li and Xie~\cite{LiX20} propose two valid inequalities for strengthening
the MISDP formulation of SPCA, i.e., upper bound ($\beta_k$) of the RIP:
\begin{align*}
  \sum_{j=1}^n X_{ij}^2 &\leq X_{ii}z_i,\quad \forall \; i \in [n],\\
  \big(\sum_{j=1}^n \abs{X_{ij}}\big)^2 &\leq kX_{ii}z_i, \quad \forall \;
                                          i \in [n].
\end{align*}
Both inequalities are SOC-representable and can thus be formulated as an SDP-constraint:
\begin{align}\label{eq:ValidSOCPineqSDP}
  \sum_{j=1}^n X_{ij}^2 \leq X_{ii}z_i \; \Leftrightarrow \;
  \begin{pmatrix}
    \tfrac{X_{ii}+z_I}{2} & X_{i1} & \cdots & X_{in} & \tfrac{X_{ii}-z_i}{2}
    \\
    X_{i1} & 1 & & 0 & 0 \\
    \vdots &\vdots & \ddots & \vdots & \vdots \\
    X_{in} & 0 & & 1 & 0 \\
    \tfrac{X_{ii}-z_i}{2} & 0 & \cdots & 0 & 1
  \end{pmatrix} \succeq 0.
\end{align}
This gives rise to the following weaker inequalities:
\begin{align*}
  \sum_{j=1}^n X_{ij}^2 \leq z_i^2 \; \Leftrightarrow \;
  \begin{pmatrix}
    z_i & X_{i1} & \cdots & X_{in} \\
    X_{i1} & 1 & & 0 \\
    \vdots &\vdots & \ddots & \vdots \\
    X_{in} & 0 & & 1
  \end{pmatrix} \succeq 0, \qquad
                   X_{ij}^2 \leq z_iX_{ii}  \; \Leftrightarrow \;
                   \begin{pmatrix}
                     z_i & X_{ij} \\
                     X_{ij} & X_{ii}
                   \end{pmatrix} \succeq 0,
\end{align*}
where the second inequality can be added for all~$0\leq j < i\leq n$.

@@

  \item ``socp'' : variant of the valid inequalities from~\cite{LiX20},
    see~\eqref{eq:ValidSOCPineqSDP}. Only for right side!
      \item 0: no valid inequalities
      \item 1: valid inequalities as SDP-constraints,
        see~\eqref{eq:ValidSOCPineqSDP}
      \item 2: valid inequalities directly as SOC-constraints

@@

    if~$A \geq 0$ entrywise), 0 (without)! Only for right side!

@@

\subsection{CBF-file for dual MISDP-formulation of RIP}
\label{sec:CBFdual}
This section describes the structure of the CBF-file for the
MISDP-formulation~\eqref{eq:MISDPRIP} in dual form (using scalar variables)
generated by
\textsf{SCIPSDP/RIP-MISDP-Paper/scripts/RIPCBFdual.m}. Note that the valid
SOCP inequality and the strengthening of the lower bounds if~$A$ is
nonnegative is only valid for the right side of the RIP! \\

@@

\# cons: $2n^2+n+2 - {\color{blue}\text{strgbnds}\cdot n^2} +
{\color{magenta} \ones_{\text{socp} = 2} \cdot n(n+2)}$, \qquad
\# cones = $5 - {\color{blue} \text{strgbnds}} + {\color{magenta}
  \ones_{\text{socp} = 2} \cdot n}$ \\
{\color{violet} If ``boundver'' = 0 : \# cons: $3n+2 - \text{strgbnds}\cdot
  n + \ones_{\text{socp} = 2} \cdot n(n+2)$} \\

@@

    &\text{L-}  &1\; {\color{violet}(1)} \qquad & \sum z_i - k \leq 0 \\
    &{\color{magenta} \text{Q}} & {\color{magenta} n+2} \qquad &
    {\color{magenta} C_i \in L_{n+2}} \qquad &
    {\color{magenta} \text{n times}}

@@

\# entries: $4n^2+3n - {\color{blue} \text{strgbnds}\cdot 2n^2} +
{\color{magenta} \ones_{\text{socp} = 2} \cdot n(n+4)}$ \\
{\color{violet} If ``boundver'' = 0 : \# entries:
  $7n - \text{strgbnds}\cdot 2n + \ones_{\text{socp} = 2} \cdot n(n+4)$. In
  this case, all constraints are only added

@@

  that $n^2$ needs to be subtracted from the first column (scalar cons $i$)
  in the fourth to seventh line.}

@@

    & n+in+j \quad & i \quad & -1.0\; (i = j),\, {\color{orange}
      -\tfrac{1}{2}\; (i\neq j)} \quad & {\color{blue}-z_j - X_{ij} \leq 0}

@@

    & n+in+j \quad & n+\tfrac{1}{2}i(i+1)+j \quad & -1.0 \quad &
    {\color{blue}-z_j - X_{ij} \leq 0} \quad & 0 \leq i,\, j \leq

@@

    & n+in+j \quad & n+\tfrac{1}{2}j(j+1)+i \quad & -1.0 \quad &
    {\color{blue}-z_j - X_{ij} \leq 0} \quad & 0 \leq i,\, j \leq

@@

    & n+n^2+in+j \quad & i \quad & 1.0\; (i = j),\, {\color{orange}
      \tfrac{1}{2}\; (i\neq j)} \quad & z_j - X_{ij} \geq 0 \quad & 0

@@

    & n+n^2+in+j \quad & n+\tfrac{1}{2}i(i+1)+j \quad & -1.0 \quad & z_j -
    X_{ij} \geq 0 \quad &

@@

    & n+n^2+in+j \quad & n+\tfrac{1}{2}j(j+1)+i \quad & -1.0 \quad & z_j -
    X_{ij} \geq 0 \quad &

@@

    i = 0,\dots,n-1 \\
    & {\color{magenta} n+2n^2+2+...} \quad &
    {\color{magenta}n+\tfrac{1}{2}i(i+1)+i} \quad & {\color{magenta}0.5}
    \quad & {\color{magenta}C_i \in L_{n+2}} \quad & {\color{magenta}i =
      0,\dots,n-1} \\
    & {\color{magenta}n+2n^2+2+...} \quad & {\color{magenta} i} \quad &
    {\color{magenta} 0.5} \quad & {\color{magenta} C_i \in L_{n+2}} \quad &
    {\color{magenta} i = 0,\dots,n-1} \\
    & {\color{magenta} n+2n^2+2+...}  \quad & {\color{magenta}
      n+\tfrac{1}{2}i(i+1)+j} \quad & {\color{magenta} 0.5} \quad  &
    {\color{magenta} C_i \in L_{n+2}} \quad & {\color{magenta} 0 \leq
      i,j\leq n-1, i \geq j} \\
    & {\color{magenta} n+2n^2+2+...}  \quad & {\color{magenta}
      n+\tfrac{1}{2}j(j+1)+i} \quad & {\color{magenta} 0.5} \quad  &
    {\color{magenta} C_i \in L_{n+2}} \quad & {\color{magenta} 0 \leq
      i,j\leq n-1, i < j} \\
    & {\color{magenta} n+2n^2+2+...}  \quad & {\color{magenta}
      n+\tfrac{1}{2}i(i+1)+i} \quad & {\color{magenta} 0.5} \quad  &
    {\color{magenta} C_i \in L_{n+2}} \quad & {\color{magenta} i =
      0,\dots,n-1} \\
    & {\color{magenta} n+2n^2+2+...}  \quad & {\color{magenta} i} \quad &
    {\color{magenta} -0.5} \quad  & {\color{magenta} C_i \in L_{n+2}} \quad
    & {\color{magenta} i = 0,\dots,n-1} \\

@@

\textbf{BCOORD} (scalar cons $i$ | val) \\
\# entries: $n+2$ \\
{\color{violet} If ``boundver'' = 0 : then all constraints are only added
  for~$i=j$, so that the first column (scalar cons $i$) changes accordingly.} \\
{\color{blue} If strgbnds = 1, then $n^2$ constraints are cancelled, so
  that $n^2$ needs to be subtracted from the first column
  (scalar cons $i$) in the second and third line.}
\[
  \begin{aligned}
    & i \quad & 1.0 \quad & -z_i + 1 \geq 0 \quad & i = 0,\dots,n-1 \\
    & n+2n^2 \quad & -1.0 \quad & \tr(X) - 1 = 0 \quad & i = 0,\dots,n-1
    \\
    & n+2n^2+1 \quad & -k  \quad & \sum z_i - k \geq 0 \quad & i =
    0,\dots,n-1
  \end{aligned}
\]
\textbf{HCOORD} (psd cons $i$ | scalar var $j$ | row | col | val) \\
\# entries: $\tfrac{1}{2}n(n+1)$ {\color{red} $(+n(n+4))$} \\
\[
  \begin{aligned}
    &0 \qquad &n+\tfrac{1}{2}i(i+1)+j \qquad &i \qquad &j \qquad &1.0
    \qquad &X \succeq 0 \qquad &0 \leq j \leq i \leq n-1 \\
    &{\color{red}i+1} \qquad &{\color{red}i} \qquad &{\color{red}0} \qquad
    &{\color{red}0} \qquad &{\color{red}\tfrac{1}{2}} \qquad
    &{\color{red}P_i \succeq 0} \qquad & \\
    &{\color{red}i+1} \qquad &{\color{red}i} \qquad &{\color{red}n+1} \qquad
    &{\color{red}0} \qquad &{\color{red}-\tfrac{1}{2}} \qquad
    &{\color{red}P_i \succeq 0} \qquad &\\
    &{\color{red}i+1} \qquad &{\color{red}n+\tfrac{1}{2}i(i+1)+i} \qquad &{\color{red}0} \qquad
    &{\color{red}0} \qquad &{\color{red}\tfrac{1}{2}} \qquad
    &{\color{red}P_i \succeq 0} \qquad &\\
    &{\color{red}i+1} \qquad &{\color{red}n+\tfrac{1}{2}i(i+1)+i} \qquad &{\color{red}n+1} \qquad
    &{\color{red}0} \qquad &{\color{red}\tfrac{1}{2}} \qquad
    &{\color{red}P_i \succeq 0} \qquad &\\
    &{\color{red}i+1} \qquad &{\color{red}i} \qquad &{\color{red}0} \qquad
    &{\color{red}0} \qquad &{\color{red}\tfrac{1}{2}} \qquad
    &{\color{red}P_i \succeq 0} \qquad &\\
    &{\color{red}i+1} \qquad &{\color{red}n+\tfrac{1}{2}i(i+1)+j} \qquad &{\color{red}j+1} \qquad
    &{\color{red}0} \qquad &{\color{red}1.0} \qquad
    &{\color{red}P_i \succeq 0} \qquad &{\color{red}0 \leq j \leq i}\\ 
    &{\color{red}i+1} \qquad &{\color{red}n+\tfrac{1}{2}j(j+1)+i} \qquad &{\color{red}j+1} \qquad
    &{\color{red}0} \qquad &{\color{red}1.0} \qquad
    &{\color{red}P_i \succeq 0} \qquad &{\color{red}i < j \leq
      n-1 }
  \end{aligned}
\]
{\color{red}\textbf{DCOORD} (psd cons $i$ | row | col | val) \\
  \# entries: $n(n+1)$\\
  \[
    \begin{aligned}
      {\color{red} i+1} \qquad & {\color{red} j+1} \qquad & {\color{red}
        1.0} \qquad & {\color{red} P_i \succeq 0} \qquad & {\color{red} i =
        0, \dots, n-1}
    \end{aligned}
    \]

@@

Options in \textsf{SCIPSDP/RIP-MISDP-Paper/scripts/RIPCBFdual.m}:
\begin{itemize}
\item If Rank = 1: \textcolor{green}{PSDCONRANK1} is added.
\item If trineq = 1: In CON the definition of the cone for the trace
  constraint is changed from~$\text{L}=$ to~\textcolor{cyan}{$\text{L-}$}
  or~\textcolor{cyan}{$\text{L}+$}, respectively.
\item If boundver = 0: The coupling constraints are only added for~$i = j$,
  i.e., {\color{violet} $-z_i \leq X_{ii} \leq z_i$, $i \in [n]$}. This
  changes the number of constraints in CON, and the number of entries in
  ACOORD, since all entries with $i \neq j$ in ACOORD need to be
  cancelled. Additionally, the first column (scalar cons $i$) in ACOORD and
  BCOORD needs to be adapted. See the changes in
  \textcolor{violet}{violet}.
\item If boundver = 2: {\color{orange}
    $-\tfrac{1}{2}z_j \leq X_{ij} \leq \tfrac{1}{2}z_j$ for $i \neq j$} is
  weakened to {\color{orange}$-z_j \leq X_{ij} \leq z_j$}, so that the
  {\color{orange} $-\tfrac{1}{2}$} is changed to $-1.0$ in ACOORD.
\item If strgbnds = 1: If A is nonnegative, then the stronger lower
  bounds~$X_{ij} \geq 0$ for all $i,j =0,\dots,n-1$ are used. See the
  changes in \textcolor{blue}{blue} for VAR, CON. Additionally, the two
  lines in ACOORD with a \textcolor{blue}{blue constraint} are cancelled
  as well. Only valid for the right side.
\item If socp = 1: The valid SOCP inequalities
  $\sum_{j=0}^{n-1}X_{ij}^2 \leq X_{ii}z_i$ for $i = 0,\dots,n-1$
  from~\cite{LiX20} are added. See the changes in PSDCON, HCOORD, DCOORD in
  \textcolor{red}{red}. These inequalities are SDP-representable via
  \begin{align*}
    \sum_{j=1}^n X_{ij}^2 \leq X_{ii}z_i \; \Leftrightarrow \;
    P_i \define \begin{pmatrix}
      \tfrac{X_{ii}+z_I}{2} & X_{i1} & \cdots & X_{in} & \tfrac{X_{ii}-z_i}{2}
      \\
      X_{i1} & 1 & & 0 & 0 \\
      \vdots &\vdots & \ddots & \vdots & \vdots \\
      X_{in} & 0 & & 1 & 0 \\
      \tfrac{X_{ii}-z_i}{2} & 0 & \cdots & 0 & 1
    \end{pmatrix} \succeq 0.
  \end{align*}
  See the last two columns in FCOORD, ACOORD, BCOORD for a description on
  how to write these inequalities in the CBF-format. Here, $E_{ij}$ is a
  symmetric matrix of suitable dimension with ones at positions $(i,j)$ and
  $(j,i)$, and zeros else. Only valid for the right side.
\item If socp = 2: The valid SOCP inequalities
  $\sum_{j=0}^{n-1}X_{ij}^2 \leq X_{ii}z_i$ for $i = 0,\dots,n-1$
  from~\cite{LiX20} are added directly as SOC-constraints, as those are
  SOC-representable:
  \begin{align*}
    C_i \define \big(X_{i1}, \dots, X_{in}, \tfrac{1}{2}(X_{ii}-z_i),
    \tfrac{1}{2}(X_{ii}+z_i \big) \in L_{n+2}.
  \end{align*}
  See the changes in CON and ACOORD in \textcolor{magenta}{magenta}.
\end{itemize}

\subsection{CBF-file for primal MISDP-formulation of RIP}
\label{sec:CBFprimal}
This section describes the structure of the CBF-file for the
MISDP-formulation~\eqref{eq:MISDPRIP} in primal form (using matrix variables)
generated by
\textsf{SCIPSDP/RIP-MISDP-Paper/scripts/RIPCBFdual.m}. Note that the valid
SOCP inequality and the strengthening of the lower bounds if~$A$ is
nonnegative is only valid for the right side of the RIP! \\

@@

\# cons:
$2n^2+n+2 +
{\color{red}\ones_{\text{socp}=1}\cdot(\tfrac{1}{2}n(n+3)(n+2))} +
{\color{magenta}\ones_{\text{socp}=2}\cdot(n(n+2))} - {\color{blue}
  \text{strgbnds} \cdot (\tfrac{1}{2}n(n-1))}$, \\
\# cones = $5 + {\color{red} \ones_{\text{socp}=1}} + {\color{magenta}
  \ones_{\text{socp}=2} \cdot n}$\\

@@

  \ones_{\text{socp}=1}\cdot(\tfrac{1}{2}n(n+3)(n+2)) +
  \ones_{\text{socp}=2}\cdot(n(n+2)) $} \\

@@

    &\text{L-}  &1 \qquad & \sum z_i - k \leq 0 \\
    &{\color{magenta} \text{Q}} & {\color{magenta} n+2} \qquad &
    {\color{magenta} C_i \in L_{n+2}} \qquad &
    {\color{magenta} \text{n times}}

@@

\# entries: $2n^2+n$ + {\color{red}
  $\ones_{\text{socp}=1} \cdot n\cdot(3n+5+\tfrac{1}{2}n(n+1))$ } +
{\color{magenta} $\ones_{\text{socp}=2} \cdot n(n+2)$ } - {\color{blue}
  $\text{strgbnds} \cdot

@@

{\color{violet} If ``boundver'' = 0: \# entries:
  $3n + \ones_{\text{socp}=1} \cdot n\cdot(3n+5+\tfrac{1}{2}n(n+1)) +
  \ones_{\text{socp}=2} \cdot n(n+2) - \text{strgbnds} \cdot

@@

{\color{red} The following entries need to be added for
  all~$i = 0,\dots,n-1$}:

@@

    \leq 0 \quad & i = 0,\dots,n-1 \\
    &{\color{magenta} n+2n^2+2+...} \quad & {\color{magenta} 0} \quad &
    {\color{magenta} i} \quad & {\color{magenta} i} \quad &
    {\color{magenta} 0.5} \quad & {\color{magenta} C_i \in L_{n+2}} \quad &
    {\color{magenta} i = 0,\dots,n-1} \\
    &{\color{magenta} n+2n^2+2+...} \quad & {\color{magenta} 0} \quad &
    {\color{magenta} i} \quad & {\color{magenta} j} \quad &
    {\color{magenta} 1.0} \quad & {\color{magenta} C_i \in L_{n+2}} \quad &
    {\color{magenta} 0 \leq i,j\leq n-1, i \geq j} \\
    &{\color{magenta} n+2n^2+2+...} \quad & {\color{magenta} 0} \quad &
    {\color{magenta} j} \quad & {\color{magenta} i} \quad &
    {\color{magenta} 1.0} \quad & {\color{magenta} C_i \in L_{n+2}} \quad &
    {\color{magenta} 0 \leq i,j\leq n-1, i < j} \\
    &{\color{magenta} n+2n^2+2+...} \quad & {\color{magenta} 0} \quad &
    {\color{magenta} i} \quad & {\color{magenta} i} \quad &
    {\color{magenta} 0.5} \quad & {\color{magenta} C_i \in L_{n+2}} \quad &
    {\color{magenta} i = 0,\dots,n-1} \\
